Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-02 writeup/gz_hubble_data.tex

In the FERENGI data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users. This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}). Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence. These galaxies are used to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which are insufficient for deriving a correction. An example of this is given in Section \ref{sec:ferengi_bar}, based on attempting to compute $\zeta$ for $p_{\rm bar}$ in Task~03. For this reason, GZH only provides debiased vote fractions for Task~01 (smooth/features/artifact).

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

>>>>

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users. This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}). Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01 (described above). The goodness-of-fit was evaluated in each bin, for each Task, using the value of the sum of the square residuals (SSR). The mean SSR for all Tasks was $\mu_{\rm SSR}$ = 0.46, $\sigma$ = 0.36, which was not considered sufficiently low in any Task for the fits to accurately model the data. An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section \ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms the available data in each bin is scattered to a degree at which no correlation may be confidently obtained. For these reasons, debiased vote fractions are only offered for Task~01 (smooth/features).  
\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}
